---
title: "3PG example"
author: "Juergen Knauer (adopted from Jinyan Yang)"
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    toc: true
    toc_float: true
    code_folding: true
---
```{r message=F, include=FALSE}
library('r3PG')
```

We will now use real data from Cumberland Plain Woodland (-33.6166, 150.7377). We need to first read in meteorology data and then obtain plant physiological parameters.

Here we will go through changing each input files (met,species,thinning and parameters).

### 1) Met data

Our site is in Richmond NSW, dominated by E.tereticornis Sm. The site has a mean annual temperature of 17 $^\circ C$ and a mean annual precipitation of 800mm.

Let’s now read and look at the met data.

```{r}
met.df <- read.csv("/Users/30044953/Downloads/ros.met.csv")

head(met.df)

met.date <- apply(met.df[,c(2,3)],1,function(x) (paste(x,collapse = "-")))
met.date <- paste0(met.date,"-15")   # append pseudo day
met.df[,"date"] <- as.Date(met.date) # append to met.df data.frame

```


```{r}
plot(met.df$prcp ~ met.df$date,xlab='',ylab = 'prcp (mm)',type="b")

plot(met.df$srad ~ met.df$date,xlab='',ylab = 'srad (MJ m-2 d-1)',type="b")
```

We need to put in number of frost days and  $CO_{2}$ data. 

```{r}
# 
met.df$frost_days <- 0
# 
met.df$co2  <- 410
met.df$srad <- 2.3 * met.df$srad  # photosynthetically active radiation to total radiation
```

### 2 Site information

```{r}
site.new <- d_site

site.new$latitude   <- -38
site.new$altitude   <- 50
site.new$soil_class <- 2
site.new$asw_min    <- 50
site.new$asw_max    <- 300
site.new$asw_i      <- 150
site.new$from       <- '2019-01'
site.new$to         <- '2021-03'
```


### 3 Species composition

Since we are using only one species, the inputs are just the initial conditions of the species.

```{r}
spc.new <- d_species[1,]
spc.new$species <- 'Eucalyptus tereticornis'
spc.new$planted <- '1900-01'
spc.new$fertility <- 1
spc.new$stems_n   <- 400
spc.new$biom_stem <- 90
spc.new$biom_root <- 10
spc.new$biom_foliage <- 0.2
```


### 4 Plant physiology

Let see if our species has been reported by previous literature.

```{r}
list.spc <- get_parameters(mode = "overview", sp_names = NULL)

euc.list <- list.spc$species[grep(pattern = 'Eucalyptus',x = list.spc$species)]

print(euc.list)
```

We did not find our species but a similar one, E.globulus. We are going to use the most of the parameters from E.globulus as example.

```{r}
## overview of available parameters
get_parameters(mode = "overview", sp_names = 'Eucalyptus globulus')

## let's select the data from Australia
params.et <- get_parameters(mode = "parameters", sp_names = 'Eucalyptus globulus 97')

# We use Pinus sylvestris as template
par.new <- d_parameters[,c("parameter","Pinus sylvestris")]
colnames(par.new)[2] <- "Eucalyptus tereticornis"

## We change a few parameters manually
par.new[par.new$parameter == "Tmin",2] <- params.et[params.et$parameter == "Tmin",2]
par.new[par.new$parameter == "Tmax",2] <- params.et[params.et$parameter == "Tmax",2]
par.new[par.new$parameter == "Topt",2] <- params.et[params.et$parameter == "Topt",2]

par.new[par.new$parameter == 'alphaCx',2] <- params.et[params.et$parameter == 'alphaCx',2]
par.new[par.new$parameter == 'SLA0',2] <- 50
par.new[par.new$parameter == 'SLA1',2] <- 50
par.new[par.new$parameter == 'CoeffCond',2] <- 0.05

par.new[par.new$parameter == 'fCalpha700',2] <- 1.8
par.new[par.new$parameter == 'fCg700',2] <- 0.6
```

### 4 Allometry and Thinning



```{r}
# We follow the workflow from above, but with 'sizeDist' instead of 'parameters'
size.et <- get_parameters(mode = "sizeDist", sp_names = 'Eucalyptus globulus 97')

head(size.et)

# It turns out there is no allometry information for Eucalyptus globulus!
# In this case, we assume the same allometry as for 'Pinus sylvestris

size.new <- d_sizeDist[,c(1,3)]
colnames(size.new)[2] <- "Eucalyptus tereticornis"

head(size.new)

```


There are other parameter files related to thinning (d_thinning).

To keep it simple, we do not account for thinning in the model. We can choose this option
by saying thinning = NULL.




Now that we have all the input files, we can run the model!

### 5 Normal run

```{r}
climate.new <- prepare_climate(met.df,from="2019-01",to="2021-03")
out.et <- run_3PG(site = site.new,
                  species = spc.new,
                  climate = climate.new,
                  thinning = NULL,
                  parameters = par.new,
                  size_dist = size.new,
                  settings = list(light_model = 2, 
                                  transp_model = 2, phys_model = 2,
                                  correct_bias = 0, calculate_d13c = 0),
                  check_input = TRUE, 
                  df_out = TRUE)


# What would have happened with more precipitation?
climate.new$co2 <- climate.new$co2 + 150
out.et.eco2 <- run_3PG(site = site.new,
                      species = spc.new,
                      climate = climate.new,
                      thinning = NULL,
                      parameters = par.new,
                      size_dist = size.new,
                      settings = list(light_model = 2, 
                                    transp_model = 2, phys_model = 2,
                                    correct_bias = 0, calculate_d13c = 0),
                      check_input = TRUE, 
                      df_out = TRUE)
```




Let's check the change in GPP. 

```{r}
par(mar=c(5,5,1,1))
plot(value~date,data = out.et.eco2[out.et.eco2$species == 'Eucalyptus tereticornis' &
                                  out.et.eco2$variable == 'gpp',],
       type='l',xlab='',ylab=expression('GPP'~(t~DM~ha^-1)),col="green")
  
  points(value~date,data = out.et[out.et$species == 'Eucalyptus tereticornis' &
                                  out.et$variable == 'gpp',],
         type='l',xlab='',col="red")
  
  legend('topleft',legend = c('eCO2','aCO2'),
         lty='solid',col=c("green","red"),bty='n',horiz = T)

```

and finally on Transpiration

```{r}
par(mar=c(5,5,1,1))
plot(value~date,data = out.et.eco2[out.et.eco2$species == 'Eucalyptus tereticornis' &
                                  out.et.eco2$variable == 'transp_veg',],
       type='l',xlab='',ylab=expression('Transpiration (mm month-1)'),col="green",
       ylim=c(0,70))
  
  points(value~date,data = out.et[out.et$species == 'Eucalyptus tereticornis' &
                                  out.et$variable == 'transp_veg',],
         type='l',xlab='',col="red")
  
  legend('topleft',legend = c('eCO2','aCO2'),
         lty='solid',col=c("green","red"),bty='n',horiz = T)

```

